Assignment 4

### 2015-03-05 rmtw/a4/latex8.tex
Added tests for H eff and H rate

>>>>

\Section{Tests for eff}

%R output start
	F test to compare two variances

data:  uc_eff and cl_eff
F = 1.61, num df = 25, denom df = 25, p-value = 0.2407
alternative hypothesis: true ratio of variances is not equal to 1
95 percent confidence interval:
 0.721893 3.590874
sample estimates:
ratio of variances 
          1.610039 
%R output end

Since the p-value is larger than 0.05, we can deduce that the variances are homogeneous (cite expe) and that the T-test is the optimal approach.

------------------------------------------------------------

%R output start
	Two Sample t-test

data:  uc_eff and cl_eff
t = -1.0786, df = 50, p-value = 0.286
alternative hypothesis: true difference in means is not equal to 0
95 percent confidence interval:
 -3.2585387  0.9816156
sample estimates:
mean of x mean of y 
 6.161538  7.300000 
 %R output end

According to the test, the efficiency of CL is 7.3 while the efficiency of UC is 6.16 and H1 eff is therefore accepted.

\Section{Tests for rate}

%R output start
	F test to compare two variances

data:  uc_rate and cl_rate
F = 1.7018, num df = 25, denom df = 25, p-value = 0.1907
alternative hypothesis: true ratio of variances is not equal to 1
95 percent confidence interval:
 0.7630304 3.7955018
sample estimates:
ratio of variances 
          1.701788 
%R output end

Since the p-value is larger than 0.05, we can deduce that the variances are homogeneous (cite expe) and that the T-test is the optimal approach.

------------------------------------------------------------

%R output start
	Two Sample t-test

data:  uc_rate and cl_rate
t = -1.1416, df = 50, p-value = 0.2591
alternative hypothesis: true difference in means is not equal to 0
95 percent confidence interval:
 -0.06525100  0.01795869
sample estimates:
mean of x mean of y 
0.1211538 0.1448000 
%R output end

According to the test, the rate of CL is 1.45 while the effectiveness of UC is 0.12 and H1 rate is therefore accepted.
